Information-Theoretic Registration with Explicit Reorientation of Diffusion-Weighted Images

### 2021-01-07 Apps/Overleaf/JMIV DWI  Registration/dwiregistering.tex
fix some notations

  H_{\bm I_{\sigma\kappa}\circ\Phi_{\bm c};\beta} \ar[ur]&  
  H_{\bm J_{\sigma\kappa};\beta}\ar[u] & 
  H_{\bm I_{\sigma\kappa}\circ\Phi_{\bm c}, \bm J_{\sigma\kappa};\beta}\ar[lu]\\
  p_{\bm I_{\sigma\kappa}\circ\Phi_{\bm c};\beta}\ar[u]  & 
  p_{\bm J_{\sigma\kappa};\beta}\ar[u]  & 
  p_{\bm I_{\sigma\kappa}\circ\Phi_{\bm c}, \bm J_{\sigma\kappa};\beta}\ar[u]\\
  ~ & h_{\bm I_{\sigma\kappa}\circ\Phi_{\bm c},\bm J_{\sigma\kappa};\beta}\ar[ul]\ar[u]\ar[ur]& ~\\

@@

  anchor={[xshift=-2.2em,yshift=2ex]center},end
  anchor={[xshift=+3.1em,yshift=2ex]center}]

@@

  anchor={[xshift=-2.2em,yshift=2ex]center},end
  anchor={[xshift=-2.2em,yshift=-1.5ex]center}]

@@

  anchor={[xshift=-2.2em,yshift=-1.5ex]center},end
  anchor={[xshift=+3.1em,yshift=-1.5ex]center}]

@@

  anchor={[xshift=+3.1em,yshift=2ex]center},end
  anchor={[xshift=+3.1em,yshift=-1.5ex]center}]

>>>>

  H_{\sigma\kappa\beta}(\bsI\circ\Phi_{\bsc}) \ar[ur]&  
  H_{\sigma\kappa\beta}(\bsJ)\ar[u] & 
  H_{\sigma\kappa\beta}(\bsI\circ\Phi_{\bsc}, \bsJ)\ar[lu]\\
  p_{\bm I\circ\Phi_{\bm c};\sigma\kappa\beta}\ar[u]  & 
  p_{\bm J;\sigma\kappa\beta}\ar[u]  & 
  p_{\bm I\circ\Phi_{\bm c}, \bm J;\sigma\kappa\beta}\ar[u]\\
  ~ & h_{\bm I\circ\Phi_{\bm c},\bm J;\sigma\kappa\beta}\ar[ul]\ar[u]\ar[ur]& ~\\

@@

  anchor={[xshift=-2.9em,yshift=2ex]center},end
  anchor={[xshift=+3.6em,yshift=2ex]center}]

@@

  anchor={[xshift=-2.9em,yshift=2ex]center},end
  anchor={[xshift=-2.9em,yshift=-1.5ex]center}]

@@

  anchor={[xshift=-2.9em,yshift=-1.5ex]center},end
  anchor={[xshift=+3.6em,yshift=-1.5ex]center}]

@@

  anchor={[xshift=+3.6em,yshift=2ex]center},end
  anchor={[xshift=+3.6em,yshift=-1.5ex]center}]
